### 2020-09-01 ongoing_draft/ongoing_paper.Rmd
yet another directory cuz I suck at gitdiff

\documentclass[doc,a4paper,man,natbib,floatsintext,noextraspace]{apa6}
<<echo=F>>=
# Set the global chunk options
set.seed(42)
knitr::opts_chunk$set(encoding = 'UTF-8',
                      cache.extra = knitr::rand_seed,
                      echo = F,
                      results = 'hide',
                      message = F,
                      warning = F)
options("citation_format" = "pandoc")
@

<<setup, echo=FALSE, cache=FALSE>>=
## numbers >= 10^5 will be denoted in scientific notation,
## and rounded to 2 digits
options(scipen = 1, digits = 2)
@

\usepackage[english]{babel}
\usepackage[utf8x]{inputenc}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{graphicx}
\usepackage[colorinlistoftodos]{todonotes}
\usepackage[singlespacing]{setspace}

<<>>=

# load packages
library(patchSynctex)
library(knitcitations)
library(car, warn.conflicts = FALSE)
library(MASS)
library(brms)
library(xtable)
library(ggpubr)
library(languageR)
library(tidyverse)
library(gdata)
library(magrittr)
library(ggplot2)
theme_set(theme_bw())

# to-do: check that the CI-computation code is up-to-date
source("../scripts/misc.R")

@
\title{The Role of Shallow Processing in Agreement Attraction}
\shorttitle{Your APA6-Style Manuscript}
\author{Utku Türk, Pavel Loga\v{c}ev}
\affiliation{Boğaziçi University}

\abstract{We report the results of two speeded acceptability judgment experiments in Turkish. We hypothesized an alternative explanation for agreement attraction effects in Turkish that is based on shallow processing. Our findings contradict our hypothesized form-driven processing strategy and support an account of agreement attraction based on the use of abstract linguistic features, rather than mere form.}

\input{settings.tex}

\begin{document}

\maketitle

\section{Introduction} \label{sec:Intro}

% %\footnote{\printglossaries}. % add this to somewhere in the first page I suppose
% 
% \subsection{Agreement Attraction Thingy} \label{sec:Intro:literature}
% 
% \subsubsection{Morphophonology} \label{sec:Intro:literature:morphophonology}
% 
% %fill here accordingly to your results AFTER YOU WRITE THE RESULT.
% 
% 
% \subsubsection{related sub-sub-field studies} \label{sec:Intro:literature:others}
% 
% \subsubsection{This work details} \label{sec:Intro:literature:thiswork}

% \citet{LagoEtAl:2018} hypothesize that genitive NPs can trigger agreement attraction in Turkish, because Turkish makes heavy use of genitive subjects, which means genitives are a priori likely to function as agreement controllers. The underlying assumption is that agreement processes rely on, at least partially, the case of an NP to determine its fit for the role of an agreement controller. 
% If that is so, their items are problematic %as in ... give an example
% in that the marking on the head noun is ambiguous between possessive and accusative case, while only possessive-marked NPs qualify as agreement controllers. Therefore, if engaged in shallow processing, readers may be more likely to misidentify the genitive NP as the agreement controller when the head noun, which is the only other alternative, is ambiguous, compared to when it is not.

% In Experiment 1, we decided to test this hypothesis

% to-do: This all needs to go up, to the description of the potential confound in Lago et al.'s study.
%This change was due to the morpho-phonologic nature of possessive suffix in Turkish, which spell-outs as (\textit{-I}) after a consonant same as the accusative.

\section{Experiment 1} \label{sec:exp1}

% do not do this in one chunk. differentiate the chunks and give them proper names.
<<>>=

@@

@@

df_merged <- dplyr::bind_rows(df_merge_exp1, df_merge_lago)
df_merged$subject %<>% as.factor()
df_merged$item %<>% as.factor()

df_exp1_na_nofillers <- subset(df_merge_exp1, is.na(ResponseYes) & source != "filler")
df_merged %<>% subset( !is.na(ResponseYes) )

@

In Experiment 1, we tested whether speakers of Turkish make fewer agreement attraction errors when the local ambiguity in the head noun is resolved. 
Specifically, we tried to replicate \citet{LagoEtAl:2018} study. However, instead of using morphologically ambiguous head nouns, we uses nouns ending in a vowel, thus resolving the ambiguity between the accusative and possessive.

\subsection{Participants} \label{sec:exp1:participants}

We recruited 118 undergraduate students to participate in Experiment 1 in exchange for course credit. All participants were native speakers of Turkish, with an average age of \Sexpr{round(mean(form_exp1$Age))} (range: \Sexpr{min(form_exp1$Age)} -- \Sexpr{max(form_exp1$Age)}).  
Experiment were carried out following the Declaration of Helsinki and the regulations concerning ethics at research in Bo\u{g}azi\c{c}i University. All participants provided informed consent prior to their participation.

\subsection{Materials} \label{sec:exp1:materials}

We used 40 sets of sentences like (\ref{item:exp1ExperimentalItems}), in which we manipulated 
(i) the number of the attractor noun, and
(ii) the number agreement on the verb. 
Plural number and plural agreement were both marked with the affix \textit{-ler/-lar}, while singular number and singular agreement were marked with its absence. 
%
We have used the experimental items in \citet{LagoEtAl:2018} as a base. 
All sentences started with a complex subject NP like \textit{`the manager's cook'} (\textit{yöneticinin aşcısı}), in which the possessor, which functioned as the attractor, carried genitive case, and the head noun carried possessive case. 
Because the head noun was singular in all conditions, sentences with plural verb agreement were ungrammatical. 
Moreover, as in the original study, the properties of the nouns in the complex subject NP and the relation between these nouns held constant in our replication. 
The distribution of the verb types followed the same pattern as in \citet{LagoEtAl:2018}, namely twenty unergatives, eighteen unaccusatives, and two optionally transitive verbs. 
Both in \citet{LagoEtAl:2018} and in our replication, pre-verbal adverbials consisting of 2-3 words (15 characters on average) are used.
Unlike the \citet{LagoEtAl:2018} sentences, our head nouns were vowel-ending, and therefore not ambiguous between accusative case, for which the case suffix is \textit{-yI}, and possessive case, for which the suffix is \textit{-sI}.

\ex. \label{item:exp1ExperimentalItems}
%
\a. \textsc{Plural Attractor, Ungrammatical (Plural Verb)} \label{item:exp1expitem-plpl}\\ 
  \gll *[Yönetici-ler-in \textbf{aşcı-sı}] mutfak-ta sürekli \textbf{zıpla-dı-lar}.\\ 
  manager-\textsc{pl}-\textsc{gen}  cook-\textsc{poss} kitchen-\textsc{loc} non-stop  jump-\textsc{pst}-\textsc{pl}.\\
  \glt \textit{`The cooks of the manager were jumping in the kitchen non-stop.'}
%
\b. \textsc{Plural Attractor, Grammatical (Singular Verb)} \label{item:exp1expitem-plsg}\\ 
  \gll [Yönetici-ler-in \textbf{aşcı-sı}] mutfak-ta sürekli \textbf{zıpla-dı}.\\ 
  manager-\textsc{pl}-\textsc{gen}  cook-\textsc{poss} kitchen-\textsc{loc} non-stop  jump-\textsc{pst}.\\
  \glt \textit{`The cooks of the manager was jumping in the kitchen non-stop.'}
%
\c. \textsc{Singular Attractor, Ungrammatical (Plural Verb)} \label{item:exp1expitem-sgpl}\\ 
  \gll *[Yönetici-nin \textbf{aşcı-sı}] mutfak-ta sürekli \textbf{zıpla-dı-lar}.\\ 
  manager-\textsc{gen}  cook-\textsc{poss} kitchen-\textsc{loc} non-stop  jump-\textsc{pst}-\textsc{pl}.\\
  \glt \textit{`The cook of the manager were jumping in the kitchen non-stop.'}
%
\d. \textsc{Singular Attractor, Grammatical (Singular Verb)}\label{item:exp1expitem-sgsg}\\ 
  \gll [Yönetici-nin \textbf{aşcı-sı}] mutfak-ta sürekli \textbf{zıpla-dı}. \\ 
  manager-\textsc{gen}  cook-\textsc{poss} kitchen-\textsc{loc} non-stop  jump-\textsc{pst}.\\
  \glt \textit{`The cook of the manager was jumping in the kitchen non-stop.'}

We intermixed our experimental sentences with 40 filler sentences of two types, as illustrated in (\ref{item:exp1FillerItems}). 
To compensate for the fact that among experimental sentences, all ungrammatical sentences ended in a plural-agreeing verb, while all grammatical sentences ended in a singular-agreeing verb, we included 20 grammatical sentences with plural verbs, and 20 ungrammatical sentences with singular agreement. 
This was done in order to discourage participants from using a strategy based on verb number. 
Filler items followed a similar template in which sentence again started with a complex genitive-possessive noun phrase. 
However, in filler items, they were the controller of an embedded clause which serves as a adverbial. 
In grammatical fillers, we have made use of pro-dropped subject strategy in Turkish; thus, it enabled us to use plural verb without having ungrammatical sentences as in (\ref{item:exp1GrammaticalFiller}). The object \textit{tutarsızlık} is a bare nominal preceding a light verb construction. 
Differently in ungrammatical fillers, bare nominal did not precede a light verb construction, but an adverb and a verb. Since Turkish only allows bare nominals right next to the verb, sentences were deemed ungrammatical when the participants read the verb.

%Even though filler items did not follow a strict template as the experimental items, they were created within a template of \textit{Noun$_{{\textsc{gen}}}$-Noun$_{{\textsc{gen}}}$-Converb-Noun-Adverb-Verb}. The ungrammaticality was created non-locally in the filler items to avoid task strategies. Example filler sentences can be seen in \ref{item:exp1FillerItems}.

\ex. \label{item:exp1FillerItems}
%
\a. \label{item:exp1GrammaticalFiller} \textsc{Grammatical Filler (Plural Verb)}\\ 
  \gll [Sosyolog-un \textbf{öğrenci-si}] konuş-unca tutarsızlık açığ-a \textbf{çıkar-dı-lar}.\\ %utku: what does this bold mean? if it the dependency between them then the bold parts are not correct. ogrencisi is the subject of the verb konusunca, and the subject of the matrix verb cikardilar is omitted.
  sociolog-\textsc{gen}  student-\textsc{poss} speak-\textsc{nmlz} inconsistency  open-\textsc{dat} deduct-\textsc{pst}-\textsc{pl}.\\
  \glt \textit{`When the student of the sociologist spoke, they revealed an inconsistency.'}
%to-do: Translation above doesn't make sense.
%
%
\b. \textsc{Ungrammatical Filler (Singular Verb)}\\ 
\gll *[Dansöz-ün \textbf{koca-sı}] var-ınca kapı sakince \textbf{aç-tı}.\\ 
dancer-\textsc{gen}  husband-\textsc{poss} arrive-\textsc{nmlz} door slowly  open-\textsc{pst}.\\
\glt \textit{Intended:`When the husband of the dancer came, the door opened slowly.'}
% to-do: Does the above mean that it's grammatical with another meaning?

\subsection{Procedure} \label{sec:exp1:procedure}

The experiment was run online, using the web-based platform Ibex Farm (\url{http://spellout.net/ibexfarm/}). Each experimental session took approximately 25 minutes to complete.
%
Prior to the start of the experiment, participants provided demographic information, as well as informed consent to participate in the experiment. They read the instructions, and were given 9 practice trials before the experiment began.
%
Each trial began with a blank screen for 600 ms, followed by a word-by-word RSVP presentation of the sentence in the center of the screen, followed by an acceptability judgment. 
Sentences were presented word-by-word in 30pt font size, and at a rate of 400 ms per word. Between each word, participants saw a blank screen for 100 ms. Participants pressed the key 'P' for \textit{'acceptable'} and 'Q' for \textit{'unacceptable'}. They were instructed to provide an acceptability rating before the 5,000 ms deadline. During the experiment, they were reminded to respond faster if they responded too slowly.

@@

\subsection{Analysis} \label{sec:exp1:analysis}

Since our aim was to test whether the morphological ambiguity present in the \citet{LagoEtAl:2018} items affected the presence or magnitude of the agreement attraction effect, statistically, we needed to test for the presence of an interaction between 
(i) the presence of the morphological ambiguity on the head noun, and 
(ii) the agreement attraction effect. 
In order to do so, we decided to analyze the data from the present experiment together with Lago et al.'s data, using experiment as an additional factor in the analysis.

%All experimental trials from both experiments (Experiment 1 and  Lago et al.'s study) was included in the analysis.

Prior to analysis we removed the data for all participants who failed to show sufficient sentitivity to the effect of grammaticality in singular attractor conditions, i.e., when no agreement attraction was expected. Specifically, we removed all participants for whom the difference in the percentage of `yes' responses between the grammatical condition \ref{item:exp1expitem-sgsg} and the ungrammatical condition \ref{item:exp1expitem-sgpl} was below the threshold of 25 percentage points. As a result, we excluded \Sexpr{length(bad_subjects)} participants from experiment 1, and \Sexpr{stopifnot(length(bad_subjects_lagoetal) == 1)} one participant from the Lago et al. data

>>>>

---
title             : "Agreement Attraction in Turkish"
shorttitle        : "Agreement Attraction in Turkish"
author: 
  - name          : "Utku Türk"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Postal address"
    email         : "utku.turk@boun.edu.tr"
affiliation:
  - id            : "1"
    institution   : "Boğaziçi University University, Istanbul, Turkey"
authornote: |
  authornote
abstract: |
  We report the results of two speeded acceptability judgment experiments in Turkish. We hypothesized an alternative explanation for agreement attraction effects in Turkish that is based on shallow processing. Our findings contradict our hypothesized form-driven processing strategy and support an account of agreement attraction based on the use of abstract linguistic features, rather than mere form.
keywords          : "keywords"
wordcount         : "X"
bibliography      : ["new-references.bib","r-references.bib"]
floatsintext      : yes
figurelist        : no
tablelist         : no
numbersections    : yes
geometry          : left=25mm, right=25mm, top=25mm, bottom=25mm
#fontsize          : 10pt
footnotelist      : no
linenumbers       : no
mask              : no
draft             : no
documentclass     : "apa6"
classoption       : "doc"
output:
  papaja::apa6_pdf:
    latex_engine: xelatex
    includes:
        in_header: paper_draft_preamble.tex
editor_options: 
  chunk_output_type: console
keep_tex: FALSE
keep_md: FALSE
---

```{r setup, eval =T, include = FALSE, message=FALSE, warning=FALSE}
library("papaja")
library(knitcitations)
library(tidyverse)
library(magrittr)
library(ggplot2)
theme_set(theme_bw())

library(car, warn.conflicts = FALE)
library(MASS)
library(brms)
library(xtable)
library(ggpubr)

library(languageR)
library(tidyverse)
library(gdata)
library(MASS)
library(magrittr)
library(ggplot2)

source("../scripts/misc.R")

```

```{r analysis-preferences, eval =T, message=FALSE, warning=FALSE}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(encoding = 'UTF-8',
                      cache.extra = knitr::rand_seed,
                      echo = FALSE,
                      results = 'asis')
options("citation_format" = "pandoc")

```

# Introduction

It has been observed that speakers often fail to accurately process grammatical dependencies between the parts of a sentence [@GibsonThomas:1999; @PhillipsEtAl:2011]. 
For example, ungrammatical center-embedded structures like  *The patient who the nurse who the clinic had hired met Jack* are found grammatical by native English speakers. 
One such comprehension error is agreement attraction [@Nicoletal:1997; @PearlmutterGarnseyBock:1999; @WagersEtAl:2009]. 
Speakers may erroneously find sentences acceptable in which the verb erroneously agrees with a syntactically unrelated noun phrase (*the attractor*) instead of the subject (*the agreement controller*) as in \@ref(item:wagers2009).

\begin{exe}
\ex \label{item:wagers2009} * The key to the cells are rusty from many years of disuse. 
\end{exe}

<!-- for some reason I could not add citation in the examples. \hfill \footnotesize{[@WagersEtAl:2009]} -->

These effects were found to be robust in a variety of constructions in different languages, e.g. English , German , Russian, Arabic, Spanish, Armenian, Slovak, Greek, and Turkish [@LagoEtAl2018; @LagoEtAl:2015; @ReifegersteEtAl:2016; @BadeckerKuminiak:2007; @TuckerEtAl:2015; @PaspaliMarinis:2020; @AvetisyanEtAl:2020] using structures like object relative clauses, subject relative clauses, possessive relative clauses, and genitive-possessive noun phrases [@LagoEtAl2018; @WagersEtAl:2009; @LagoEtAl:2015; @FranckColonnaRizzi:2015; @TuckerEtAl:2015; @ParkerEtAl:2015; @Dillon2013a; @Haussler2009]. These effects are found both in grammatical marking of the gender and the number [@BadeckerKuminiak:2007; @Slioussar:2016; @PaspaliMarinis:2020], and attested with various methods including maze tasks, ERP, eye tracking to name a few [@TannerEtAl:2014; @WagersEtAl:2009; @Nicoletal:1997].

One instance of agreement attraction is found in the production processes in which participants were asked to complete sentence fragments [@Bock1991]. Participants used the wrong verb more often when the attractor (*cabinets*) were plural, and the agreement controller (*key*) were singular as in \@ref(item:bock1991).

\begin{exe}
\ex The key to the cabinets \ldots 
\label{item:bock1991}
\end{exe}

Agreement attraction is also found in the comprehension studies. In these studies, agreement attraction is found either as a facilitation in reading times or as a effect in the acceptability rates [@WagersEtAl:2009]. 
When reading times are checked, they found that the participants read the ungrammatical sentences with a plural attractor easier then the ungrammatical sentences without a plural attractor. 
Similarly, participants found ungrammatical sentences with a plural attractor acceptable more often than that of with a singular attractor.

Some theories [@EberhardEtAl:2005; @HammerlyEtAl:2019] explain this phenomenon through a faulty representation of the number on the head of the agreement controller whereas other theories assume that agreement attraction is due to an error in the access to the number of the agreement controller [@WagersEtAl:2009; @NicenboimEtAl:2018].

Agreement attraction effects can equally well be explained by assuming shallow processing. Recent studies in psychology literature show that in certain environments people may not notice ungrammaticalities in a sentence or may not compute dependencies in a sentence completely [@OteroKintsch:1992; @FerreiraBaileyFerraro:2002].

To investigate this possibility, we report two speeded acceptability judgment experiments in this paper. The first one inspects the recent @LagoEtAl2018 findings. They found number attraction effects in genitive-possessive constructions such as `_[[the child's] toy]_' ([[_çocuğ-un\textsubscript{Gen}_] _oyuncağ-ı\textsubscript{Poss}_]). They justify the use of this construction with the findings of @NicolEtAl:2016. Since the genitive case is a possible subject marker, the participants can consider genitive marked attractors a candidate for the agreement controller. However, case marking on all subject heads is locally ambiguous the accusative and the possessive. In our experiment 1, we disambiguate the subject head and test whether or not the results were due to the shallow processing of the head subject and sticking with the accusative marked representation under some conditions.

In experiment 2, we test whether or not the agreement attraction effects in Turkish are due to form-driven processing strategy. Instead of processing the whole sentence, participants develop a mental shortcut, matching the form-identical number marking on the attractor and the matrix verb in the Turkish case, specific to the task in hand. We used the verbs of the object relative clauses as an attractor and speculated that if the participants are using the mentioned task-specific strategy, we would see comparable agreement attraction effects.

This paper is organized as \ldots

# Theories of agreement attraction

The difference between the theories that explain the agreement attraction phenomenon lies in the assumption regarding the origin of the illusion. Some theories [@BockEberhard:1993; @ViglioccoEtAl:1995; @Eberhard:1997; @FranckEtAl:2002; @BergenGibson:2012] explain this phenomenon by hypothesizing that the representations formed from the linguistic input is faulty. One theory in this group is Marking and Morphing Theory. MMT suggests that the subject phrase can hold a continuous number value from 1 (unambiguously plural) to -1 (unambiguously singular). This value is affected by the _percolation_ of the grammatical feature which can happen in any direction. The implementation of such models suggests that the final number of the phrase depends on the number morphology on the head and the elements within the phrase, and the syntactic proximity of these elements to the root node of the phrase.

Another type of model within this family is based on the idea that linguistic input is noisy, and it is accompanied by a priori linguistic knowledge [@BergenGibson:2012]. This account is an extension of the noisy channel model proposed by @Levy2008, which uses Bayesian inference to model the participants' inference given the word string. @PatsonHusband:2016 provide additional evidence for this type of analysis by showing that final interpretations of agreement attraction cases are not based on the actual string, meaning that the participants infer a plural-marked head noun whereas it is not marked by any plural inflection.

On the other side, some theories assume that agreement attraction is due to an error in the access to the number of the agreement controller [@WagersEtAl:2009; @NicenboimEtAl:2018]. Unlike MMT, these models do not assume an erroneous representation to form. Rather, the agreement attraction effects surface when there is a feature interference in the ungrammatical sentences like \@ref(item:wagers2009). This interference is triggered due to the partial match between the sought retrieval cues and the ones within the subject phrase. On some occasions, when there is no single item matching the necessary cues from the verb, number related matching cue from the attractor may satisfy the retrieval.

# Agreement Attraction in Turkish

Recently, @LagoEtAl2018 demonstrated comparable agreement attraction effects in comprehension with Turkish stimuli. 
They used the speeded acceptability judgment method with the following question that asks participants whether or not the sentence sounded acceptable. 
They used sentences like (\@ref(item:LagoExp))\footnote{Abbreviations used in the paper are as follows: \printglossaries} with genitive-marked attractors.
They manipulated the number morphology on the attractor (plural x singular) and the grammaticality of the verb (grammatical (SG) x ungrammatical (PL)). The example given here represents all four conditions.  
In an ungrammatical condition with a plural attractor, the word _ressamların_ (painters') is expected to create a grammaticality illusion and mistaken for the agreement controller instead of the head subject _rakibi_ (rival\textsubscript{poss}).

\begin{exe}
\ex \label{item:LagoExp}
\gll Ressam-$\emptyset$/lar-(n){\i}n rakib-i at\"{o}lye-den h{\i}zla uzakla\c{s}-t{\i}-$\emptyset$/lar.\\
painter-\Sg{}/\Pl{}-\Gen{} rival-\Poss{} workshop-\Abl{} quickly walked.away-\Pst{}-\Sg{}/\Pl{}\\
\glt `The painter's/painters' rival walked\textsubscript{sg/pl} away from the workshop quickly.'
\end{exe}

Following previous work on agreement attraction, they
argue
that non-intervening genitive marked attractor may create grammaticality illusions in Turkish. They base their argument on the inhibition constraint proposed by @NicolEtAl:2016. @NicolEtAl:2016 show in a production experiment that genitive attractors do not trigger grammaticality illusions. According to their hypothesis, the reason behind their results is the fact that the participants may never consider genitive-marked NPs as a potential candidate for subjects.
However, this is not the case in Turkish. In embedded sentences, the definite subject is always marked with the genitive case, which makes the genitive-marked NPs a candidate for the subjecthood in Turkish.

However, a potential complication in interpreting these results is the fact that all head nouns in Lago et al.'s stimuli were morphologically ambiguous between possessive and accusative case. This ambiguity is the result of the consonant-ending subject head usage. In Turkish, both the accusative case and the possessive surface as -I. \footnote{Throughout the paper, we present the archiphonemes with the capitalized form of the symbol. The suffix -I can surface as \textit{-i, -ı, -u, -ü}. }
Because of this local ambiguity, all experimental sentences have two possible parses up until to the end of the sentence. Check the following examples in \@ref(parse:LagoExpAcc) and \@ref(parse:LagoExpPoss).

\begin{exe}
\ex \label{parse:LagoExpAcc}
\gll [\textsubscript{CP}[\textsubscript{CP}Ressam-lar-{\i}n rakib-i at\"{o}lye-den h{\i}zla uzakla\c{s}-t{\i}ğ-{\i}n-{\i}] bil-iyor-um.]\\
painter-\Pl{}-\Gen{} rival-\Acc{} workshop-\Abl{} quickly walked.away-\Nmlz{}-\Poss{}-\Acc{} know-\Prog{}-\Fsg{}.\\
\glt `I know that the painters' rival walked away from the workshop quickly.'
\ex \label{parse:LagoExpPoss}
\gll [\textsubscript{CP}Ressam-lar-{\i}n rakib-i at\"{o}lye-den h{\i}zla uzakla\c{s}-t{\i}.]\\
painter-\Pl{}-\Gen{} rival-\Poss{} workshop-\Abl{} quickly walked.away-\Pst.\Tsg{}.\\
\glt `the painters' rival walked away from the workshop quickly.'
\end{exe}

The local ambiguity between the accusative and the possessive is not resolved until the verb _uzaklaştı_. Regardless of the assumption for parallel or serial processing, there may exist certain conditions where participants are stuck with a rival-\Acc{} representation. Since accusative number agreement controllers are extremely rare, while genitive agreement controllers are very frequent in Turkish, the ambiguity of the head noun may occasionally render the genitive modifier a stronger contender for being the agreement controller, resulting in agreement attraction. The problem with such cases for the Inhibition hypothesis is that it is not clear whether the possible non-subjecthood clue from the accusative case plays a role or the possible subjecthood clue from the genitive case plays a role.

# Experiment 1

```{r Exp1:DataWrangling, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}

@@

```

```{r Exp1:wordFreq, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
# word frequencies: 
# Utku: are these still relevant for us?

@@

df_merged <- dplyr::bind_rows(df_merge_exp1, df_merge_lago)
df_merged$subject %<>% as.factor()
df_merged$item %<>% as.factor()
```

Previous work in agreement attraction found significant effects in comprehension using forced-choice acceptability judgment tasks [@HammerlyEtAl:2019; @LagoEtAl2018; @WagersEtAl:2009]. The goal of experiment 1 is to control for the effect of head noun ambiguity on the magnitude of agreement attraction effect. To this end, we replicated @LagoEtAl2018 experiment with unambiguous head nouns. We disambiguated the cases by using vowel-ending head nouns. When attached to a vowel-ending noun, the accusative case and the possessive surface with a different floating consonant. For example, we changed sentence (\@ref(item:LagoExpContrast)) to sentence (\@ref(item:OurExpContrast)).

\begin{exe}
\ex \label{item:LagoExpContrast}
\gll Şarkıcı-$\emptyset$/lar-(n)ın vokalist-i sahne-de sürekli zıpla-dı-$\emptyset$/lar.\\
singer-\Sg{}/\Pl{}\Gen{} vocalist-\Poss{} stage-\Loc{} non-stop jump-\Pst{}-\Sg{}/\Pl{}\\
\glt `The singer's/singers' backup vocalist jumped\textsubscript{sg/pl} on the stage non-stop.'

\ex \label{item:OurExpContrast}
\gll Yönetici-$\emptyset$/ler-(n)in aşçı-sı mutfak-de sürekli zıpla-dı-$\emptyset$/lar.\\
manager-\Sg{}/\Pl{}\Gen{} cook-\Poss{} kitchen-\Loc{} non-stop jump-\Pst{}-\Sg{}/\Pl{}\\
\glt `The manager's/managers' cook jumped\textsubscript{sg/pl} in the kitchen non-stop.'
\end{exe}

We hypothesized that if the morpho-phonological ambiguity, thus the Inhibition from the accusative case, was a key factor in agreement attraction in Turkish, resolving it should diminish the attraction affects. This would tell us that readers may indeed get affected by local ambiguities which may serve as a supporting point for shallow processing.

## Participants

We recruited 118 undergraduate students to participate in Experiment 1 in exchange for course credit. All participants were native speakers of Turkish, with an average age of `r printnum(mean(form_exp1$Age))` (range: `r min(form_exp1$Age)` -- `r max(form_exp1$Age)`).  
Experiment were carried out following the Declaration of Helsinki and the regulations concerning ethics at research in Bo\u{g}azi\c{c}i University. All participants provided informed consent prior to their participation.

## Materials

We used 40 sets of sentences like \@ref(item:exp1ExperimentalItems), in which we manipulated 
(i) the number of the attractor noun, and
(ii) the number agreement on the verb. 
Plural number and plural agreement were both marked with the affix \textit{-ler/-lar}, while singular number and singular agreement were marked with its absence. 
We have used the experimental items in @LagoEtAl2018 as a base. 
All sentences started with a complex subject NP like \textit{`the manager's cook'} (\textit{yöneticinin aşcısı}), in which the possessor, which functioned as the attractor, carried genitive case, and the head noun carried unambiguous possessive case. 
Because the head noun was singular in all conditions, sentences with plural verb agreement were ungrammatical. 
Moreover, as in the original study, the properties of the nouns in the complex subject NP and the relation between these nouns held constant in our replication. 
The distribution of the verb types followed the same pattern as in @LagoEtAl2018, namely twenty unergatives, eighteen unaccusatives, and two optionally transitive verbs. 
Both in @LagoEtAl2018 and in our replication, pre-verbal adverbials consisting of 2-3 words (15 characters on average) are used. We changed this adverbials for plausability reasons, such that with head nouns like cooks we used locational adverbs like kitchen, instead of the stage.
Unlike the @LagoEtAl2018 sentences, our head nouns were vowel-ending, and therefore not ambiguous between accusative case, for which the case suffix is \textit{-yI}, and possessive case, for which the suffix is \textit{-sI}.

\begin{exe}
\ex \label{item:exp1ExperimentalItems}
  \begin{xlist}

  \ex \textsc{Plural Attractor, Ungrammatical (Plural Verb)} \label{item:exp1expitem-plpl} 
  \gll *[Yönetici-ler-in \textbf{aşcı-sı}] mutfak-ta sürekli \textbf{zıpla-dı-lar}.\\ 
  manager-\textsc{pl}-\textsc{gen}  cook-\textsc{poss} kitchen-\textsc{loc} non-stop  jump-\textsc{pst}-\textsc{pl}.\\
  \glt \textit{`The cooks of the manager were jumping in the kitchen non-stop.'}

\ex \textsc{Plural Attractor, Grammatical (Singular Verb)} \label{item:exp1expitem-plsg} 
  \gll [Yönetici-ler-in \textbf{aşcı-sı}] mutfak-ta sürekli \textbf{zıpla-dı}.\\ 
  manager-\textsc{pl}-\textsc{gen}  cook-\textsc{poss} kitchen-\textsc{loc} non-stop  jump-\textsc{pst}.\\
  \glt \textit{`The cooks of the manager was jumping in the kitchen non-stop.'}

\ex \textsc{Singular Attractor, Ungrammatical (Plural Verb)} \label{item:exp1expitem-sgpl} 
  \gll *[Yönetici-nin \textbf{aşcı-sı}] mutfak-ta sürekli \textbf{zıpla-dı-lar}.\\ 
  manager-\textsc{gen}  cook-\textsc{poss} kitchen-\textsc{loc} non-stop  jump-\textsc{pst}-\textsc{pl}.\\
  \glt \textit{`The cook of the manager were jumping in the kitchen non-stop.'}

\ex \textsc{Singular Attractor, Grammatical (Singular Verb)}\label{item:exp1expitem-sgsg}
  \gll [Yönetici-nin \textbf{aşcı-sı}] mutfak-ta sürekli \textbf{zıpla-dı}. \\ 
  manager-\textsc{gen}  cook-\textsc{poss} kitchen-\textsc{loc} non-stop  jump-\textsc{pst}.\\
  \glt \textit{`The cook of the manager was jumping in the kitchen non-stop.'}
  \end{xlist}
\end{exe}

We intermixed our experimental sentences with 40 filler sentences of two types, as illustrated in \@ref(item:exp1FillerItems). 
To compensate for the fact that among experimental sentences, all ungrammatical sentences ended in a plural-agreeing verb, while all grammatical sentences ended in a singular-agreeing verb, we included 20 grammatical sentences with plural verbs, and 20 ungrammatical sentences with singular agreement. 
This was done in order to discourage participants from using a strategy based on verb number. 
Filler items followed a similar template in which sentence again started with a complex genitive-possessive noun phrase. 
However, in filler items, they were the controller of an embedded clause which serves as a adverbial. 
In grammatical fillers, we have made use of pro-dropped subject strategy in Turkish; thus, it enabled us to use plural verb without having ungrammatical sentences as in \@ref(item:exp1GrammaticalFiller). The object \textit{tutarsızlık} is a bare nominal preceding a light verb construction. 
Differently in ungrammatical fillers, bare nominal did not precede a light verb construction, but an adverb and a verb. Since Turkish only allows bare nominals right next to the verb, sentences were deemed ungrammatical when the participants read the verb.

\begin{exe}
\ex \label{item:exp1FillerItems}
\begin{xlist}
\ex \textsc{Grammatical Filler (Plural Verb)} \label{item:exp1GrammaticalFiller}
\gll [Sosyolog-un \textbf{öğrenci-si}] konuş-unca tutarsızlık açığ-a \textbf{çıkar-dı-lar}.\\ 
sociolog-\textsc{gen}  student-\textsc{poss} speak-\textsc{nmlz} inconsistency  open-\textsc{dat} deduct-\textsc{pst}-\textsc{pl}.\\
\glt \textit{`When the student of the sociologist spoke, they revealed an inconsistency.'}

\ex \textsc{Ungrammatical Filler (Singular Verb)}
\gll *[Dansöz-ün \textbf{koca-sı}] var-ınca kapı sakince \textbf{aç-tı}. \\
dancer-\textsc{gen}  husband-\textsc{poss} arrive-\textsc{nmlz} door slowly  open-\textsc{pst}.\\
\glt \textit{Intended:`When the husband of the dancer came, the door opened slowly.'}
\end{xlist}
\end{exe}

## Procedure

The experiment was run online, using the web-based platform Ibex Farm (\url{http://spellout.net/ibexfarm/}). Each experimental session took approximately 25 minutes to complete.

Prior to the start of the experiment, participants provided demographic information, as well as informed consent to participate in the experiment. They read the instructions, and were given 9 practice trials before the experiment began.

Each trial began with a blank screen for 600 ms, followed by a word-by-word RSVP presentation of the sentence in the center of the screen, followed by an acceptability judgment. 
Sentences were presented word-by-word in 30pt font size, and at a rate of 400 ms per word. Between each word, participants saw a blank screen for 100 ms. Participants pressed the key 'P' for \textit{'acceptable'} and 'Q' for \textit{'unacceptable'}. They were instructed to provide an acceptability rating before the 5,000 ms deadline. During the experiment, they were reminded to respond faster if they responded too slowly.

@@

## Analysis

Since our aim was to test whether the morphological ambiguity present in the @LagoEtAl2018 items affected the presence or magnitude of the agreement attraction effect, statistically, we needed to test for the presence of an interaction between
(i) the presence of the morphological ambiguity on the head noun, and 
(ii) the agreement attraction effect. 
In order to do so, we decided to analyze the data from the present experiment together with Lago et al.'s data, using experiment as an additional factor in the analysis.

Prior to analysis we removed the data for all participants who failed to show sufficient sentitivity to the effect of grammaticality in singular attractor conditions, i.e., when no agreement attraction was expected. Specifically, we removed all participants for whom the difference in the percentage of 'yes' responses between the grammatical condition \@ref(item:exp1expitem-sgsg) and the ungrammatical condition \@ref(item:exp1expitem-sgpl) was below the threshold of 25 percentage points. As a result, we excluded `r length(bad_subjects)` participants from experiment 1, and `r stopifnot(length(bad_subjects_lagoetal) == 1)` one participant from the Lago et al. data

We used the R packages brms [@brms] and rstan [@stan] to fit Bayesian hierarchical models [e.g., @GelmanHill2007]. We analyzed only experimental sentences, and used 
(i) grammaticality of the sentence, 
(ii) attractor number, and 
(iii) presence of morphological ambiguity (i.e., experiment), as well as all their interactions as predictors. 
Moreover, we used by-participant and by-item intercepts and slopes for all predictors.
Data for experiment 1, along with our analysis scripts can be found in \url{https://github.com/utkuturk/replication_lagoetal2018}.

## Results
